The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-09 paper.tex
update

% 2. North Polar Spur is not shown as it is a supernova remanent near us.
  Third, the innermost bubbles, even though with high column density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$ -- $10$ eV\
  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
  This is the reason why the innermost bubbles is unseen in the observation.

>>>>

% 2. North Polar Spur is not shown as it is a supernova remanent near us.
  Third, the innermost bubbles\
  shown in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp},\
  even though with high column density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$ -- $10$ eV\
  (see the temperature slice in \Cref{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
  This is the reason why the innermost bubbles is unseen in the observation.
